Forecasting hourly hospital admission

### 2021-10-21 paper/paper.Rmd
JB paper addition
JB text addition

1. We develop a novel methodology to forecast short-term hourly hospital admission using the family of Generalised Additive Models that accounts for i) ..., ii) ... iii) , ... iv)

2. We produce probabilistic forecast, in addition to the point estimation, that quantify uncertainties in future hospital admission and we evaluate its accuracy using ...;

@@

@@

@@

Empirical distribution for same hour-of-day and day-of-week as target time.

@@

@@

>>>>

1. We produce probabilistic forecasts, in addition to the point estimation, which quantify uncertainties in future hospital admission, and compare different forecasting methods using a suite of established evaluation metrics;

2. We develop a novel approach to forecast day-ahead hourly hospital admission using Generalised Additive Models for Location Scale and Shape, which accounts for i) the bounded and non-Gaussian distribution of admissions, ii) multiple seasonalities, weather and holiday effects, and  iii) variation in forecast uncertainty;

@@

We develop a range of models for forecasting hospital admissions using a multi-year dataset. In order to facilitate model development and testing, we divide the data into a training period. We use cross-validation to iteratively fit, evaluate and develop models using the training data, before settling on their optimal configuration and testing them on the as-yet unseen test data.

Forecast are produced/issue at midnight and mid-day for lead-times from 0 to 48 hours-ahead on a rolling basis. In order to compare both parametric and non-parametric probabilistic forecasts, we evaluate quantiles of the predictive distribution at probability level 0.05, 0.10,... 0.95, as well as the expectation.

@@

The data we use in this case study are from hospital XYZ, and comprises records of arrivals at Accident and Emergentcy at hourly granularity. The training data runs from 01/04/2014 to 28/02/2018, and the test data runs from 1/3/2018 to 28/2/2019.

@@

The first benchmark we consider is to simply use the empirical distribution of past observations as a probabilistic forecast for same hour-of-day and day-of-week that we are forecasting. This is often called `climatology'. However, as we observe a trend in the data used here, we re-calculate the climatology on a rolling basis using the most recent one-year of data in order to track the trend.

@@

## Model fits

### Truncated Normal GAMLSS Model

**Not sure if this should stay here, but interesting and worth reporting, I think...**

Plot smooth functions estiamted for time of day, day of year, for both mean and variance parameters.

@@

Forecast performance by time of day...
